Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-25 sections/eval.tex
Update on Overleaf.

Given this language, we now describe how to define a few example functions from the API as plans in the Finch Logic language,
\begin{align*}
\text{sum(M, dims=[2])} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchrelabel(M, i_1,\ldots,i_d), i_2)), out)\\
\text{matmul(A, B)} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchmapjoin(*, \finchrelabel(A, i, j), \finchrelabel(B, j, k)), j)), out)\\
\end{align*}
Notably, these plans do not specify

>>>>

Given this language, we now describe how to define a few example functions from the API as plans in the Finch Logic language,
\begin{align*}
\text{sum(M, dims=[2])} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchrelabel(M, i_1,\ldots,i_d), i_2)), out)\\
\text{matmul(A, B)} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchmapjoin(*, \finchrelabel(A, i, j), \finchrelabel(B, j, k)), j)), out)\\
\end{align*}
Notably, these plans do not specify important details about the computation such as the format of intermediates and the order of the loops. In the following discussion, we provide sensible heuristics and show that they provide good performance on important kernels. However, for larger or more complex programs, it would be important to apply a cost-based optimization
